\huge Open, privacy-preserving protocols for lawful surveillance

### 2016-02-29 paper/conc.tex
changes to latest version of paper

For contact chaining, it may be possible to speed up our protocols by using
elliptic-curve cryptography instead of RSA.  It may also be interesting to 
generalize the differential-privacy approach of Kearns {\it et 
al.}~\cite{krwy-pnas16} so that it applies to indirect contacts as well as
direct contacts.

>>>>

For contact chaining, it may be possible to speed up our protocols by using
elliptic-curve cryptography instead of RSA. Additionally, our assumption that
all parties behave in an honest-but-curious manner might be weakened. By using
standard zero-knowledge proof techniques, it might be possible to create versions
of the protocols in Section~\ref{sec-chaining} that are secure against, for
example, a rogue agent's maliciously modifying telecom-supplied data in order
to falsely incriminate a victim. It may also be interesting to 
generalize the differential-privacy approach of Kearns {\it et 
al.}~\cite{krwy-pnas16} so that it applies to indirect contacts as well as
direct contacts.

### 2016-02-29 paper/intro.tex
changes to latest version of paper

We draw a distinction between law enforcment access to
third-party records held by businesses such as telephone companies,
and encrypted information stored on an individual's personal devices:
our work focuses on the former, not the latter.
In particular, we believe that lawful searches of third-party records
can be made much more security- and privacy-preserving than they currently are
without compromising law enforcement search capabilities.
We are {\em not} suggesting support for ``key escrowed'' encryption
or general backdoors in personal devices,
as is the topic of the ongoing conflict between the FBI and Apple.

Adopting the approach to third-party records search
taken by Bandits~\cite{sff-foci2014}\footnote{Throughout this submission, we
cite an anonymized version of an existing paper on accountable surveillance
and use the pseudonym ``Bandits'' instead of the names of the authors.}, we
seek to design and implement protocols for {\it accountable surveillance}.
We require that government surveillance be conducted according to {\it open
processes}, as defined in Section~\ref{sec-open} below, and that the privacy
of {\it untargeted users} be protected.  We consider the surveillance goals
of {\it set intersection} and {\it contact chaining} and show that both can 
be achieved in a privacy-preserving, accountable fashion.

>>>>

We draw a distinction between law-enforcement access to
third-party records held by businesses such as telephone companies
and encrypted information stored on an individual's personal devices;
our work focuses on the former, not the latter.
In particular, we believe that lawful searches of third-party records
can be made much more security- and privacy-preserving than they currently are
without compromising law-enforcement search capabilities.
We are {\em not} suggesting support for ``key escrowed'' encryption
or general backdoors in personal devices,
as is the topic of the ongoing conflict between the FBI and Apple.

Adopting the approach to third-party records search
taken by Bandits~\cite{sff-foci2014}\footnote{Throughout this submission, we
cite an anonymized version of an existing paper on accountable surveillance
and use the pseudonym ``Bandits'' instead of the names of the authors.}, we
seek to design and implement protocols for {\it accountable surveillance}.
We require that government surveillance be conducted according to {\it open
processes}, as defined in Section~\ref{sec-open} below, and that the privacy
of {\it untargeted users} be protected.  We consider the surveillance goals
of {\it set intersection} and {\it contact chaining}~\cite{techdirt} and show that both can 
be achieved in a privacy-preserving, accountable fashion.

### 2016-02-29 paper/submission.tex
changes to latest version of paper

  \begin{abstract}
{The question of how government agencies can
acquire actionable, useful information about legitimate but unknown targets 
without intruding upon the electronic activity of innocent parties is 
extremely important.  We address this question by providing experimental
evidence that actionable, useful information can indeed be obtained in a manner
that preserves the privacy of innocent parties and that holds government
agencies accountable.  In particular, we present practical, privacy-preserving
protocols for two operations that law-enforcement and intelligence agencies
have used effectively: {\it set intersection} and {\it contact chaining}.
Experiments with our protocols suggest
that privacy-preserving contact chaining can perform
a 3-hop privacy-preserving graph traversal producing 27,000 ciphertexts
in under two minutes.
These ciphertexts are usable in turn via private set
intersection to pinpoint potential unknown targets within a body of 150,000
total ciphertexts within 10 minutes,
without exposing personal information about non-targets.
}
  \end{abstract}
  \keywords{Privacy, Secure multiparty computation, Surveillance}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

@@

\begin{thebibliography}{99}
%\bibitem{journal-1} A.~P.~Raposo, H.~J.~Weber, D.~E.~Alvarez--Castillo, M.~Kirchbach, Cent. Eur. J. Phys. 5, 253 (2007)
%\bibitem{journal-2} J.~Barth et al. (SAPHIR Collaboration), Phys. Lett. B 572, 127 (2003)
%\bibitem{journal-3} S.~Chekanov et al., Eur. Phys. J. C 51, 289 (2007)
%\bibitem{journal-4} K.~Malarz, Postepy Fizyki 57, 235 (2006) (in Polish)
%\bibitem{journal-5} G.~Meng, Cent. Eur. J. Phys., DOI:10.2478/s11534-007-0038-1
%\bibitem{journal-6} R.~Hegselmann, U.~Krause, Journal of Artificial Societies and Social Simulation (2006), https://urldefense.proofpoint.com/v2/url?u=http-3A__jasss.soc.surrey.ac.uk_9_3_10.html&d=AwIGaQ&c=-dg2m7zWuuDZ0MUcV7Sdqw&r=TO0xacJWWmvm7m0roFn_liAsIL2PkxELeLGL8JNJXFw&m=Ka2FvolwqKNW8vu0FjJrZZz-0NBFnF_Zu-dQp-fjTto&s=370GY1pBTDyr9NSQToGqkNR8K-Xy1z0bsX64GpcLiPk&e= 
%\bibitem{journal-7} A.~Dybala, Cent. Eur. J. Chem. (in press)
%\bibitem{journal-8} A.~Dybala, Przeglad chemiczny (in Polish, in press)
%\bibitem{book} M.~Lister, Fundamentals of Operating Systems, 3rd edition (Springer-Verlag, New York, 1984)
%\bibitem{chapter} C.~K.~Clenshaw, K.~Lord, In: B.~K.~P.~Scaife (Ed.), Studies in Numerical Analysis (Academic Press, London and New York, 1974) 95
%\bibitem{arxiv-1} M.~Majewski, K.~Malarz, arXiv:cond-mat/0609635v2 [cond-mat.stat-mech]
%\bibitem{arxiv-2} J.~A.~C.~E.~Solano, arXiv:0707.1343v1 [astro-ph]
%\bibitem{sff-foci2014} A.~Segal, B.~Ford, J.~Feigenbaum, 
%In: J. Crandall and V. Paxson (Eds.), $4^{th}$ Workshop on Free and 
%Open Communications on the Internet, August 18, 2014, San Diego, 
%USA (USENIX, Berkeley, 2014)

\bibitem{sff-foci2014} Bandits, Catching Bandits and Only Bandits:
Privacy-Preserving Intersection Warrants for Lawful Surveillance,
\url{https://drive.google.com/file/d/0BwK1bcoczINtbUhPaFI0Mk1DVk0/view}
(2016)

>>>>

  \begin{abstract}
{The question of how government agencies can
acquire actionable, useful information about legitimate but unknown targets 
without intruding upon the electronic activity of innocent parties is 
extremely important.  We address this question by providing experimental
evidence that actionable, useful information can indeed be obtained in a manner
that preserves the privacy of innocent parties and that holds government
agencies accountable.  In particular, we present practical, privacy-preserving
protocols for two operations that law-enforcement and intelligence agencies
have used effectively: {\it set intersection} and {\it contact chaining}.
Experiments with our protocols suggest
that privacy-preserving contact chaining can perform
a 3-hop privacy-preserving graph traversal producing 27,000 ciphertexts
in under two minutes.
These ciphertexts are usable in turn via privacy-preserving set
intersection to pinpoint potential unknown targets within a body of 150,000
total ciphertexts within 10 minutes,
without exposing personal information about non-targets.
}
  \end{abstract}
  \keywords{Privacy, Secure multiparty computation, Surveillance}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

@@

\begin{thebibliography}{99}
%\bibitem{journal-1} A.~P.~Raposo, H.~J.~Weber, D.~E.~Alvarez--Castillo, M.~Kirchbach, Cent. Eur. J. Phys. 5, 253 (2007)
%\bibitem{journal-2} J.~Barth et al. (SAPHIR Collaboration), Phys. Lett. B 572, 127 (2003)
%\bibitem{journal-3} S.~Chekanov et al., Eur. Phys. J. C 51, 289 (2007)
%\bibitem{journal-4} K.~Malarz, Postepy Fizyki 57, 235 (2006) (in Polish)
%\bibitem{journal-5} G.~Meng, Cent. Eur. J. Phys., DOI:10.2478/s11534-007-0038-1
%\bibitem{journal-6} R.~Hegselmann, U.~Krause, Journal of Artificial Societies and Social Simulation (2006), https://urldefense.proofpoint.com/v2/url?u=http-3A__jasss.soc.surrey.ac.uk_9_3_10.html&d=AwIGaQ&c=-dg2m7zWuuDZ0MUcV7Sdqw&r=TO0xacJWWmvm7m0roFn_liAsIL2PkxELeLGL8JNJXFw&m=Ka2FvolwqKNW8vu0FjJrZZz-0NBFnF_Zu-dQp-fjTto&s=370GY1pBTDyr9NSQToGqkNR8K-Xy1z0bsX64GpcLiPk&e= 
%\bibitem{journal-7} A.~Dybala, Cent. Eur. J. Chem. (in press)
%\bibitem{journal-8} A.~Dybala, Przeglad chemiczny (in Polish, in press)
%\bibitem{book} M.~Lister, Fundamentals of Operating Systems, 3rd edition (Springer-Verlag, New York, 1984)
%\bibitem{chapter} C.~K.~Clenshaw, K.~Lord, In: B.~K.~P.~Scaife (Ed.), Studies in Numerical Analysis (Academic Press, London and New York, 1974) 95
%\bibitem{arxiv-1} M.~Majewski, K.~Malarz, arXiv:cond-mat/0609635v2 [cond-mat.stat-mech]
%\bibitem{arxiv-2} J.~A.~C.~E.~Solano, arXiv:0707.1343v1 [astro-ph]

%\bibitem{sff-foci2014} A.~Segal, B.~Ford, J.~Feigenbaum, 
%In: J. Crandall and V. Paxson (Eds.), $4^{th}$ Workshop on Free and 
%Open Communications on the Internet, August 18, 2014, San Diego, 
%USA (USENIX, Berkeley, 2014)

\vskip 2\baselineskip %needed to compile correctly

\bibitem{sff-foci2014} Bandits, Catching Bandits and Only Bandits:
Privacy-Preserving Intersection Warrants for Lawful Surveillance,
February 2016 \url{https://drive.google.com/file/d/0BwK1bcoczINtbUhPaFI0Mk1DVk0/view}
